### 2018-03-16 submission/manuscript.Rmd
update and change first section of results

***The Number of OTUs is Dependent on HiFi DNA Polymerase:***
There was a HiFi DNA polymerase dependent difference that was consistent across sub-sampling [Figure 1]. Lower cycle numbers (15-20) tended to result in less differences between HiFI DNA polymerase versus higher cycle numbers (25, 30, and 35)  [Figure 1]. At 35 cycles, all sub-sampling levels had significant differences between HiFi DNA polymerases (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. Some differences between HiFi DNA polymerase we identifed at 25 and 30 cycles but the sub-sampling depth had to be 5000 or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Most of the differences observed at 35 cycles were between Platinum and other HiFi DNA polymerases, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2]

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples with the same DNA polymerases having high (Platinum) and low (Accuprime) number of OTUs [Figure 2 & Table S3]. In contrast to fecal samples, differences between HiFi DNA polymerase were observed as early as 20 cycles and as low as a sub-sampling depth of 1000 sequences (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. For both different cycle numbers and sub-sampling depths, the majority of differences were between Platinum and the other HiFi DNA polymerases [Table S4]. The lowest number of OTUs identified was from Accuprime^TM^ while the highest was from Platinum and this was consistent for both fecal and mock samples across sub-sampling depth and cycle number [Figure 1 & 2]. Based on these observations it is clear that different HiFi DNA polymerase result in different total number of OTUs observed within a sample.

>>>>

***The Number of OTUs are Dependent on HiFi DNA Polymerase:***
A consistent difference in the number of OTUs, that was dependent on the HiFi DNA polymerase used was observed regardless of sub-sampling depth for fecal samples [Figure 1]. Additionally, there was a trend for lower cycle numbers (15-20) to result in less differences in the number of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA polymerases [Figure 1]. For fecal samples, all sub-sampling levels had significant differences between HiFi DNA polymerases at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. Most of the differences observed at 35 cycles were between Platinum and other HiFi DNA polymerases, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2]. Differences in the number of OTUs between HiFi DNA polymerases were identifiable at earlier cycles (25 and 30) but the sub-sampling depth had to be 5000 sequences or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1].

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same HiFi DNA polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across cycle number and sub-sampling depth [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between HiFi DNA polymerases were observed as early as 20 cycles and at as low of a sub-sampling depth as 1000 sequences in the mock community samples (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. For both cycle numbers and sub-sampling depths, the majority of  differences in the number of OTUs were between Platinum and the other HiFi DNA polymerases [Table S4]. Based on these observations in fecal and mock communities, it is clear that different HiFi DNA polymerases result in a different total number of OTUs observed within a sample.

### 2018-03-16 submission/manuscript.tex
update and change first section of results

\textbf{\emph{The Number of OTUs is Dependent on HiFi DNA Polymerase:}}
There was a HiFi DNA polymerase dependent difference that was consistent
across sub-sampling {[}Figure 1{]}. Lower cycle numbers (15-20) tended
to result in less differences between HiFI DNA polymerase versus higher
cycle numbers (25, 30, and 35) {[}Figure 1{]}. At 35 cycles, all
sub-sampling levels had significant differences between HiFi DNA
polymerases (P-value \textless{} 0.0001) {[}Table S1{]}. Some
differences between HiFi DNA polymerase we identifed at 25 and 30 cycles
but the sub-sampling depth had to be 5000 or higher (P-value \textless{}
0.05) {[}Table S1{]}. Most of the differences observed at 35 cycles were
between Platinum and other HiFi DNA polymerases, based on a Tukey
post-hoc test (P-value \textless{} 0.05) {[}Table S2{]}

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples with the same DNA
polymerases having high (Platinum) and low (Accuprime) number of OTUs
{[}Figure 2 \& Table S3{]}. In contrast to fecal samples, differences
between HiFi DNA polymerase were observed as early as 20 cycles and as
low as a sub-sampling depth of 1000 sequences (P-value = 0.002) {[}Table
S3{]}. For both different cycle numbers and sub-sampling depths, the
majority of differences were between Platinum and the other HiFi DNA
polymerases {[}Table S4{]}. The lowest number of OTUs identified was
from Accuprime\textsuperscript{TM} while the highest was from Platinum
and this was consistent for both fecal and mock samples across
sub-sampling depth and cycle number {[}Figure 1 \& 2{]}. Based on these
observations it is clear that different HiFi DNA polymerase result in
different total number of OTUs observed within a sample.

>>>>

\textbf{\emph{The Number of OTUs are Dependent on HiFi DNA Polymerase:}}
A consistent difference in the number of OTUs, that was dependent on the
HiFi DNA polymerase used was observed regardless of sub-sampling depth
for fecal samples {[}Figure 1{]}. Additionally, there was a trend for
lower cycle numbers (15-20) to result in less differences in the number
of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA
polymerases {[}Figure 1{]}. For fecal samples, all sub-sampling levels
had significant differences between HiFi DNA polymerases at 35 cycles
(P-value \textless{} 0.0001) {[}Table S1{]}. Most of the differences
observed at 35 cycles were between Platinum and other HiFi DNA
polymerases, based on a Tukey post-hoc test (P-value \textless{} 0.05)
{[}Table S2{]}. Differences in the number of OTUs between HiFi DNA
polymerases were identifiable at earlier cycles (25 and 30) but the
sub-sampling depth had to be 5000 sequences or higher (P-value
\textless{} 0.05) {[}Table S1{]}.

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples {[}Figure 2{]}. Regardless
if fecal or mock communities were used, the same HiFi DNA polymerases
had high (Platinum) and low (Accuprime) number of OTUs and this was
consistent across cycle number and sub-sampling depth {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between HiFi DNA polymerases were observed as early as 20
cycles and at as low of a sub-sampling depth as 1000 sequences in the
mock community samples (P-value = 0.002) {[}Table S3{]}. For both cycle
numbers and sub-sampling depths, the majority of differences in the
number of OTUs were between Platinum and the other HiFi DNA polymerases
{[}Table S4{]}. Based on these observations in fecal and mock
communities, it is clear that different HiFi DNA polymerases result in a
different total number of OTUs observed within a sample.
